Review: Crop adaptation through introgression from wild relatives

### 2016-08-01 TiG_prospectus.tex
Li added modification

Second, local ancestry reconvolution (also known as chromosome painting) can identify the genomic regions that come from different source populations \cite{schraiber2015}. 
Such method usually takes phased haplotypes as input and an exception is MULTIMIX \cite{churchhouse2013}, which can take both phased and unphased haplotypes as input. and unveil the genomic ancestry from multiple source populations.

@@

>>>>

Second, local ancestry reconvolution (also known as chromosome painting) can identify the genomic regions that come from different source populations \cite{schraiber2015}. 
Such method usually takes phased haplotypes as input and an exception is MULTIMIX \cite{churchhouse2013}, which can take both phased and unphased haplotypes as input, and unveil the genomic ancestry from multiple source populations.

@@

Fourth, structure related approaches are based on the popular software STRUCTURE \cite{pritchard2000}, which provided an estimate of fraction of each individual's genome coming from each population. 
Many approaches in this respect have been developed.
Two of them, fineStructure \cite{Lawson2012} and Globetrotter \cite{hellenthal2014}, were selected as representations.
Different from STRUCTURE, fineStructure not only identifies the number of populations but also estimates the probability that genomic regions belong to one or the other populations. 
Globotrotter is a development of fineStructure at tracing back to an unsampled source population and at dating the admixture events.
